%Section: Work Experience at the top
\sectionTitle{Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
  {April 2024}   {Data Visualisation of Climate Change}{Python}{UK}
  {} {
    \begin{itemize}
      \item Dissertation based on visualising climate change data using Python libraries and researching the data based off of graphs created. Has a basic UI using Tkinter.
    \end{itemize}
  }
  {Python, Plotly, Pandas, Tkinter}
  \emptySeparator
  \experience
  {March 2024}   {AI Chatbot}{Python}{UK}
  {} {
    \begin{itemize}
      \item A project creating a chatbot that implements AI techniques. The topic of the chatbot was based around fruits and was tasked with implementing conversational capabilities (pattern-based and similarity-based) using AIML, and lemmatisation, tf/idf, and cosine similarity methods. Also adding rule-based logical reasoning using FOL knowledgebase and NLTK library which could be updated or queried. And finally, image classification capabilities training a CNN model to detect images of fruit.
    \end{itemize}
  }
  {Python, AIML, NLP, Similarity Methods, NLTK, FOL, CNN}
  \emptySeparator
  \experience
  {March 2024}   {Mobile Applications}{Java}{UK}
  {} {
    \begin{itemize}
      \item Tasked with creating a mobile application of my choice and decided to create a “ToDoList” application which would allow users to create tasks, modify tasks, and delete them. 
      Developed with Java using Android Studio
    \end{itemize}
  }
  {Java, Android Studio, Firebase}
  \emptySeparator
  \experience
  {March 2022}   {Front-end Web Design}{HTML/CSS}{UK}
  {} {
    \begin{itemize}
      \item Developed HTML and CSS code for a group project for a smart refrigerator application.

    \end{itemize}
  }
  {HTML, CSS, GitHub, Teamwork}
  \emptySeparator
  \experience
  {January 2024}   {Developing a RESTful Web Service }{Python}{UK}
  {} {
    \begin{itemize}
      \item A project to create an application named “Travel Buddy Finder”. This involved implementing a RESTful web service, designed to run on a local or remote server using frameworks like Spring Boot. Each action in the application is exposed as a REST method, and communication between the users and the server is done via JSON. Once this program was completed, I was tasked with cloud migration and deployed the program on Azure’s Virtual Machine resource. Once this was completed testing was conducted using Locust.
      \item GitHub Link: https://github.com/IsaacPrkr/TripProject-Travel-Buddy-App
    \end{itemize}
  }
  {Python, RESTful Framework, JSON, Azure, Locust}
  \emptySeparator
\end{experiences}
